---
title: "Modern Times Fortunate Island"
output: github_document
---

Recipe is adapted from [BYO's Barley Brown’s Brewing Co.’s Turmoil Cascadian Dark Ale clone](https://byo.com/article/specialty-ipa-layout/).

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/black ipa/brewlog_batch1.xml'
boiloff_rate_override = 4
#hop_price_override = 10.25

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

Water Information
=================

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 150ppm
    * Chloride: 150ppm
    * Mash pH: 5.34
* Water Additions:
    * 2.2g Gypsum
    * 4.25g Calcium Chloride (3.3g, but since it's 77%, 4.25g)
    * 7g Epsom Salt
    * 2ml Lactic Acid (80%) 
    * 3.2g Salt
* Adjusted Water Profile:
    * Calcium: 113ppm
    * Magnesium: 30ppm
    * Sodium: 50ppm
    * Sulfate: 152ppm
    * Chloride: 155ppm
    * Bicarbonate: 166ppm
    * Estimated Mash pH: 5.46

Brew Notes
==========



Post Notes
==========

Bottling Notes (2018/08/05)
==========================




