---
title: "Mad Fermentiationist's Red Rye IPA"
output: github_document
---

Original recipe from [here](https://www.themadfermentationist.com/2012/08/india-red-rye-ale-recipe.html) and [here](https://www.themadfermentationist.com/2013/04/three-modern-times-west-test-batches.html), [mine](https://www.brewersfriend.com/homebrew/recipe/view/907558/madfermentationist-s-leftovers-red-rye-ipa)

```{r setup-variables, echo=FALSE}

boiloff_rate_override = 4.0
brewlog_file = '../recipes/red rye ipa/brewlog_2019-11-11.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```


Water Information
=================

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 150ppm
    * Chloride: 150ppm
    * Mash pH: 5.30
* Water Additions:
    * 2.2g Gypsum
    * 4.4g Calcium Chloride (3.4g, but since it's 77%, 4.4g)
    * 7.3g Epsom Salt
    * 5.9ml Lactic Acid (80%)
    * 3.4g Salt
* Adjusted Water Profile:
    * Calcium: 113ppm
    * Magnesium: 30ppm
    * Sodium: 50ppm
    * Sulfate: 152ppm
    * Chloride: 155ppm
    * Bicarbonate: 66ppm
    * Estimated Mash pH: 5.30

Preparation Notes
=================

Brew Notes
==========

Post Brew Notes
===============


Bottling Notes (2018-07-27)
===========================


