---
title: "Mad Fermentiationist's Red Rye IPA"
output: github_document
---

Original recipe from [here](https://www.themadfermentationist.com/2012/08/india-red-rye-ale-recipe.html) and [here](https://www.themadfermentationist.com/2013/04/three-modern-times-west-test-batches.html), [mine](https://www.brewersfriend.com/homebrew/recipe/view/701488/madfermentationist-s-red-rye-ipa)

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/red rye ipa/brewlog_2018-09-07.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```


Water Information
=================

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 150ppm
    * Chloride: 150ppm
    * Mash pH: 5.35
* Water Additions:
    * 1.5g Gypsum
    * 2.99 Calcium Chloride (2.3g, but since it's 77%, 2.99g)
    * 4.9g Epsom Salt
    * 4.0ml Lactic Acid (80%)
    * 2.3g Salt
* Adjusted Water Profile:
    * Calcium: 113ppm
    * Magnesium: 30ppm
    * Sodium: 50ppm
    * Sulfate: 152ppm
    * Chloride: 155ppm
    * Bicarbonate: 66ppm
    * Estimated Mash pH: 5.36

Preparation Notes
=================

Modified Hopstand schedule and shorter boil/mash time: 30 minutes. 19 Liters in the kettle for mashing.

Brew Notes
==========



Post Brew Notes
===============


Bottling Notes (2018-07-27)
===========================


Related Article/References
==========================

