---
title: "Mad Fermentiationist's Red Rye IPA"
output: github_document
---

Original recipe from [here](https://www.themadfermentationist.com/2012/08/india-red-rye-ale-recipe.html) and [here](https://www.themadfermentationist.com/2013/04/three-modern-times-west-test-batches.html), [mine](https://www.brewersfriend.com/homebrew/recipe/view/672949/madfermentationist-s-red-rye-ipa)

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/red rye ipa/brewlog_2018-07-08.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```


Water Information
=================

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 150ppm
    * Chloride: 150ppm
    * Mash pH: 5.35
* Water Additions:
    * 1.5g Gypsum
    * 2.99 Calcium Chloride (2.3g, but since it's 77%, 2.99g)
    * 4.9g Epsom Salt
    * 4.0ml Lactic Acid (80%)
    * 2.3g Salt
* Adjusted Water Profile:
    * Calcium: 113ppm
    * Magnesium: 30ppm
    * Sodium: 50ppm
    * Sulfate: 152ppm
    * Chloride: 155ppm
    * Bicarbonate: 66ppm
    * Estimated Mash pH: 5.36

Preparation Notes
=================

* Need to check for sodium: http://brulosophy.com/2018/01/22/water-chemistry-pt-10-the-impact-of-sodium-on-beer-exbeeriment-results/. Probably 50ppm would be sufficient.
* https://beerandbrewing.com/make-your-best-rye-ipa-beer-recipe/
* http://beerandwinejournal.com/rye-ipa/
* https://www.seriouseats.com/recipes/2011/04/red-ale-for-beginning-homebrewers-hoppy-red-ale-recipe.html

Brew Notes
==========

* (11h50) Started setting up, filling 19 Liters of strike water and milling.
* (12h50) Mash in (took longer than usual because kettle wasn't at max). Strike temp 66.5, got down to 65.1 with grains.
* (13h50) Getting grains out. Wort is at 64C. Preboil gravity at 1.038 at 60.3 degrees.
* (13h10) Wort at 75.6, wort is at 18.2cm in the kettle.
* (14h37) Wort is boiling (took more time, because kettle wasn't at max), put 24g of 14.6% AA Columbus.
* (15h40) Stopped kettle, started chilling to target temp of 70C for hop stand. Added 81g of 13.9% AA Simcoe at 70C for 30 minutes.
* (16h22) Started immersion chiller.
* (16h37) Put wort in fermentor at 27.5 degrees. I didn't put the yeast yet. I put the wort in the basement in an insulation jacket with ice bottles. This will allow the wort to go at reasonable pitching temp. 1.064 OG at 27.5C.
* (16h50) Cleanup almost done.
* (23h50) Pitching yeast at 17.5C.