---
title: "Coffee Oatmeal Stout"
output: github_document
---

This recipe is a clone of Modern Times' Black House. Original recipe is [here](https://www.themadfermentationist.com/2012/06/toasted-oat-coffee-stout.html). I used [brewer's friend](https://www.brewersfriend.com/) website to adjust [my recipe](https://www.brewersfriend.com/homebrew/recipe/view/682652/coffee-oatmeal-stout-preparation).

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/coffee oatmeal stout/brewlog.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```


Water Information
=================

Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html) Water Profile:

* Calcium(Ca): 104.0 ppm
* Magnesium(Mg): 15.0 ppm
* Sodium(Na): 64.0 ppm
* Sulfate(SO4): 102.0 ppm
* Chloride(Cl): 76.0 ppm
* biCarbonate(HCO3): 280.0 ppm

Target Water Profile:

* Sodium: 50.0 ppm
* Sulfate: 100.0 ppm
* Chloride: 75.0 ppm
* Mash pH: 5.35

Water Additions:

* Gypsum: 1.6g
* Calcium Cloride: 0g
* Epsom Salt: 2.6g
* Lactic Acid (80%): 1ml
* Table Salt (non-iodized): 2.4g

Resulting Water:

* Calcium(Ca): 69.0 ppm
* Magnesium(Mg): 17.0 ppm
* Sodium(Na): 50 ppm
* Sulfate(SO4): 102 ppm
* Chloride(Cl): 77 ppm
* Bicarbonate: 135 ppm
* Mash pH: 5.40

Preparation Notes
=================

* https://byo.com/article/brewing-with-oatmeal-2/

Recipe Changes
==============

* Roasted Barley is belgian and is higher than the original's 300L roasted barley. I'll keep the percentages and see what it will give
* I replaced the chocolate malt by Chocolate Rye.
* I replaced the crystal 90L by CaraRye.
* I might need to find a better replacement for Maris Otter.
