---
title: "Mad Fermentiationist's Big Hop IPA"
output: github_document
---

This is my interpretation of Pliny the Elder's recipe. This is inspired from MadFermentationist's [own interpretation](https://www.themadfermentationist.com/2010/12/pliny-younger-clone-recipe.html) and his own [DIPA Bomb recipe](https://www.themadfermentationist.com/2010/02/big-ipa-recipe-1-lb-of-hops.html), [mine](https://www.brewersfriend.com/homebrew/recipe/view/686156/imperial-ipa-almost-)

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/imperial ipa/brewlog.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```


Water Information
=================

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 150ppm
    * Chloride: 150ppm
    * Mash pH: 5.35
* Water Additions:
    * 1.5g Gypsum
    * 2.99 Calcium Chloride (2.3g, but since it's 77%, 2.99g)
    * 4.9g Epsom Salt
    * 4.5ml Lactic Acid (80%)
    * 2.3g Salt
* Adjusted Water Profile:
    * Calcium: 113ppm
    * Magnesium: 30ppm
    * Sodium: 50ppm
    * Sulfate: 152ppm
    * Chloride: 155ppm
    * Bicarbonate: 66ppm
    * Estimated Mash pH: 5.36
