---
title: "Mad Fermentiationist's Big Hop IPA"
output: github_document
---

This is my interpretation of Pliny the Elder's recipe. This is inspired from MadFermentationist's [own interpretation](https://www.themadfermentationist.com/2010/12/pliny-younger-clone-recipe.html) and his own [DIPA Bomb recipe](https://www.themadfermentationist.com/2010/02/big-ipa-recipe-1-lb-of-hops.html), [mine](https://www.brewersfriend.com/homebrew/recipe/view/686156/imperial-ipa-almost-)

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/imperial ipa/brewlog_2018-08-23.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```


Water Information
=================

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 150ppm
    * Chloride: 150ppm
    * Mash pH: 5.35
* Water Additions:
    * 1.5g Gypsum
    * 2.99 Calcium Chloride (2.3g, but since it's 77%, 2.99g)
    * 4.9g Epsom Salt
    * 4.5ml Lactic Acid (80%)
    * 2.3g Salt
* Adjusted Water Profile:
    * Calcium: 113ppm
    * Magnesium: 30ppm
    * Sodium: 50ppm
    * Sulfate: 152ppm
    * Chloride: 155ppm
    * Bicarbonate: 66ppm
    * Estimated Mash pH: 5.36

Brew Notes (2018/08/23)
=======================

* Grains where crushed fine. Also, I put the whole milled grains bag at the same time. This caused a giant dough ball.
* Strike water was at 68.5. Had to stir to break that giant dough ball. Temp lowered to 64.6 before I managed to cover the kettle.
* Every fit in the kettle, there's still space left for 1 liter.
* (20h18) 35 minutes mash, mash ended at 63.5C. 
* (20h18) Started kettle
* (20h57) Boil started
* (21h28) Stopped kettle fire. Put hop.
* (21h30) I took a sample but too realy. I lost a lot of hop in that sample which won't contribute to the beer.
* (21h45) Put second batch of hop)
* (22h00) Started immersion chiller
* (22h08) Put wort in fermentor at 32C, 14L.
* (22h10) FG 1.088 at 30C
* Sparkled dry yeast directly without rehydrating

Hops (To Put in notes)
======================

* 27 g columbus 14.6 + 10g columbus 13.1
* 30 g simcoe 13.9 + 30g 13.9
* 60 g cascade 6.6

Post Notes
==========

* 2018/09/29 - Got the fermentor out of the fridge, but after 6 hours, it was bubling too strongly. Decided to put it back in the fridge to let continue fermentation at low temp (17C).
* 2018/09/02 - Got the fermentor out of the fridge to finish fermentation.
* 2018/09/03 - Beer at 21C, still bubling but weakly that first time I got it out of fridge.
* I used Micheal Tonsmeire's hop aroma protocol: at flame out add half the hop, then 15 minutes later add the second one. This protocol is took from Mitch Steele. One other protocol that mitch suggest is for the dry hop: 12 days and then 3 days, removing the previous hop. I wonder if this isn't more valid for commercial brewers. TODO: add references.
* Hop loose for first dry hop batch, in a bag for the second one.
* (2018/09/15) Cold crashing

Bottling Notes (2018/09/17)
===========================

* FG 1.0.10 at 17.8C
* Targeting 3.0 CO2 volume, using 20C as highest fermentation temperature. This gives 7.7g of sugar per liter. (post note: this might have been too much). Estimated 11L of wort in the blottling bucket from the 14L that were in the fermenter. 11*7.7 = 84.7g, mesured 85g of sugar. Transfer gave 10L in the blotting bucket.
* Bottles: 11x330mL, 12x500mL.

To Read
=======

* https://byo.com/article/oh-say-can-you-c-a-guide-to-brewing-hoppy-american-pale-ales/
* https://www.homebrewersassociation.org/news/new-england-ipa-haze-craze/
* https://beergraphs.com/bg/973-two-brewers-admit-their-methods-for-haze/
* https://byo.com/article/awardwinning-ipa-recipes/
* https://www.homebrewersassociation.org/how-to-brew/5-tips-on-brewing-ipas-from-mitch-steele/
