---
title: "Zymurgy Magazine's Stout Trousers"
output: github_document
---

* https://www.brewersfriend.com/homebrew/recipe/view/659037/stout-trousers
* https://www.homebrewersassociation.org/homebrew-recipe/stout-trousers/
* https://byo.com/article/american-stout-style-profile/
* Water profile from Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html)

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/american stout/brewlog.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

Water Information
-----------------

Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html) Water Profile:

* Calcium(Ca): 104.0 ppm
* Magnesium(Mg): 15.0 ppm
* Sodium(Na): 64.0 ppm
* Sulfate(SO4): 102.0 ppm
* Chloride(Cl): 76.0 ppm
* biCarbonate(HCO3): 280.0 ppm

Target Water Profile:

* Sodium: 50.0 ppm
* Sulfate: 100.0 ppm
* Chloride: 75.0 ppm
* Mash pH: 5.2

Water Additions:

* Gypsum: 1.2g
* Calcium Cloride: 0g
* Epsom Salt: 1.9g
* Lactic Acid (80%): 3.2ml
* Table Salt (non-iodized): 1.7g

Resulting Water:

* Calcium(Ca): 69.0 ppm
* Magnesium(Mg): 17.0 ppm
* Sodium(Na): 50 ppm
* Sulfate(SO4): 102 ppm
* Chloride(Cl): 77 ppm
* Bicarbonate: 28 ppm
* Mash pH: 5.27

Preparation Notes
-----------------

* Used Bru'N'Water spreadsheet to be able to calculate sodium additions. Essentially, I decided to 
* Form BYO's article: <blockquote>All-grain brewers can use a single infusion mash and a low enough mash temperature so that the resulting beer does not end up too viscous. A temperature range of 148 to 154 °F (64 to 68 °C) works well. Use a lower mash temperature when using lower attenuating yeasts or high starting gravities and use a higher temperature when using the higher attenuating yeasts or lower starting gravity beers.</blockquote> This means that since I use Safale US-04, which is low attenuating, I'll use a low mash temperature; 65C should be enough. _Wasn't temp just bullshit?_
* Cara60 will be substituted by CaraRye. (check with Michael Tonsmeire comment) <blockquote>CARARYE® can be used to impart typical rye flavors and aromas, with the characteristic malty and spicy notes.  Intense aromas of bread, coffee, dark chocolate and dried fruit also come through.</blockquote>
* Will add lactic acid and salts before heating (from Bru'N'Water): <blockquote>For best result, add acids prior to heating the water since heating can drive off a portion of the alkalinity that the acid addition was calculated to remove.</blockquote>
* As original recipe mentions, I'll target a 5.2 mash water pH (4.8 strike water pH).
* I didn't have chocolate malt as mentionned in the recipe, but I had chocolate rye and chocolate wheat. I decided to try chocolate rye, because it said to lend more a "milk chocolate" taste, and I wanted to see what it gave in there (and was affraid to push too much on the coffee/chocolate). From BYO's [Chocolate Malt article](https://byo.com/article/chocolate-malt/): <blockquote>Chocolate rye (~250 °L) and chocolate wheat (~400 °L) are the two biggest non-barley chocolate malts. Although similar to chocolate malt made from barley, the rye version has more spiciness and milk chocolate quality. The wheat version has more of a pronounced dark chocolate character.</blockquote>Note however that with the "chocolate malt", which is described as "roasted nut", maybe it would be nice not to have too many tastes and the same time. We'll see.

Questions
---------

* There's a little bit less sodium that target profile.
    * Is this a problem
    * How can I add sodium (http://brulosophy.com/2018/01/22/water-chemistry-pt-10-the-impact-of-sodium-on-beer-exbeeriment-results/)?
    * https://www.themadfermentationist.com/2008/09/i-think-that-water-treatment-has-made.html
* Why 100 minutes of boil?
    * https://byo.com/article/boiling-advanced-brewing/
    * https://www.homebrewsupply.com/learn/60-90-otherwise-finding-best-boil-time.html
    * https://www.homebrewtalk.com/forum/threads/longer-boil-better-beer.295106/
* Right pH?
    * https://byo.com/article/the-dark-secrets-of-stout/
    * http://www.madalchemist.com/archives/mashing-the-perfect-sweet-stout/