---
title: "American Rye Stout"
output: github_document
---

This is the [third iteration](./brewlog_2018-10-19.md) of [Zymurgy Magazine's Stout Trousers](https://www.homebrewersassociation.org/homebrew-recipe/stout-trousers/). However, this time around the recipe is highly modified (to a point where it doesn't bear any resemblance) to become an American Rye Stout. This recipe was built and adjusted with [Brewer's Friend website](https://www.brewersfriend.com/homebrew/recipe/view/895830/american-rye-stout). The water profile adjustment by reading Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html) recipe.

The first recipe had a thin mouthfeel. To remedy that I decided to confirm a tendency this recipe had, meaning using rye as a "body builder".

I simplified the recipe (rounder quantities) and I lowered down the IBU so that it's calculated as 30 minutes boil, but IBU will be higher because of the nochill method (calculate 40 minutes as mentionned below).

```{r setup-variables, echo=FALSE}

boiloff_rate_override = 4.0
brewlog_file = '../recipes/american stout/brewlog_2019-10-19.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

Water Information
=================

Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html) Water Profile:

* Calcium(Ca): 104.0 ppm
* Magnesium(Mg): 15.0 ppm
* Sodium(Na): 64.0 ppm
* Sulfate(SO4): 102.0 ppm
* Chloride(Cl): 76.0 ppm
* biCarbonate(HCO3): 280.0 ppm

Target Water Profile:

* Sodium: *100.0 ppm*
* Sulfate: 100.0 ppm
* Chloride: *150 ppm*
* Mash pH: 5.32

Water Additions:

* Gypsum: 2.2
* Calcium Cloride: 0g
* Epsom Salt: 3.5g
* Lactic Acid (80%): 2.8ml
* Table Salt (non-iodized): 6.5g

Resulting Water:

* Calcium(Ca): 69.0 ppm
* Magnesium(Mg): 17.0 ppm
* Sodium(Na): 97 ppm
* Sulfate(SO4): 102 ppm
* Chloride(Cl): 150 ppm
* Bicarbonate: 100 ppm
* Estimated Mash pH: 5.32

Related Article/References
==========================

* Forum Question: [https://www.homebrewersassociation.org/forum/index.php?topic=7780.0](What hops with rye?)

Recipe Changes
==============

* In this batch, I'll use starsan in the jerry can before putting the hop. This way, I'll just put the jerry can right away in the river to cool down (and not fear infection).

Notes
=====


Brewing Notes
=============



Bottling Notes (2019/11/07)
===========================

Used dishwasher to clean bottles. Used starsan for desinfecting, but might just use the diswasher next time.

* FG: 1.018 at 27C
* 15.5L gave 20x750mL
* 7x15.5L, 108.5g of sugar
