---
title: "American Stout"
output: github_document
---

This recipe is inspired from [Zymurgy Magazine's Stout Trousers](https://www.homebrewersassociation.org/homebrew-recipe/stout-trousers/), was built and adjusted with [Brewer's Friend website](https://www.brewersfriend.com/homebrew/recipe/view/668590/stout-trousers). The recipe adjustment were made with help of the following [Brew You Own](https://byo.com/)'s article: [American Stout Style Profile](https://byo.com/article/american-stout-style-profile/). Also, I made the water profile adjustment by reading Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html) recipe.

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/american stout/brewlog_2018-06-28.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

Water Information
=================

Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html) Water Profile:

* Calcium(Ca): 104.0 ppm
* Magnesium(Mg): 15.0 ppm
* Sodium(Na): 64.0 ppm
* Sulfate(SO4): 102.0 ppm
* Chloride(Cl): 76.0 ppm
* biCarbonate(HCO3): 280.0 ppm

Target Water Profile:

* Sodium: 50.0 ppm
* Sulfate: 100.0 ppm
* Chloride: 75.0 ppm
* Mash pH: 5.35

Water Additions:

* Gypsum: 1.5g
* Calcium Cloride: 0g
* Epsom Salt: 2.5g
* Lactic Acid (80%): 2ml
* Table Salt (non-iodized): 2.3g

Resulting Water:

* Calcium(Ca): 69.0 ppm
* Magnesium(Mg): 17.0 ppm
* Sodium(Na): 50 ppm
* Sulfate(SO4): 102 ppm
* Chloride(Cl): 77 ppm
* Bicarbonate: 59 ppm
* Mash pH: 5.37

Recipe Changes
==============

Right now I'm estimating mash efficiency at 65%, even though last brew I've done had 75% efficiency. This means that the current recipe undershoot the ABV, but then if I have a higher ABV, I'll probably endup with the actual desired, but if I get 65% efficiency, I can either boil longer or accept a lower ABV.

I didn't have Carafa II as mentionned in the recipe (I only had Carafa Special II, which isn't the same thing), but since I had chocolate rye, I decided to go with this. It's said to lend more a "milk chocolate" taste, and I wanted to see what it gave in there. Next time I might try with Chocolate Wheat. From BYO's [Chocolate Malt article](https://byo.com/article/chocolate-malt/): <blockquote>Chocolate rye (~250 &deg;L) and chocolate wheat (~400 &deg;L) are the two biggest non-barley chocolate malts. Although similar to chocolate malt made from barley, the rye version has more spiciness and milk chocolate quality. The wheat version has more of a pronounced dark chocolate character.</blockquote>We'll see what it'll give, but I suspect that Carafa II would have lending more bitterness, which might be what is desired for this style. Note also that in this recipe I also have [Brewferm's Chocolate malt](https://www.brouwland.com/en/our-products/brewing/malts-and-flakes/roasted-malts/brewferm-chocolate-900-ebc/d/barley-malt-brewferm-chocolate-900-ebc-25-kg)^[I saw somewhere that brewferm was in fact from Castle Malting], which is described as "roasted nut". We'll see how this will mix togheter. We'll see.

Cara60 will be substituted by CaraRye. Weyermann's webpage description: <blockquote>CARARYE&reg; can be used to impart typical rye flavors and aromas, with the characteristic malty and spicy notes.  Intense aromas of bread, coffee, dark chocolate and dried fruit also come through.</blockquote> We'll see what it gives.

Preparation Notes
=================

* Used Bru'N'Water spreadsheet to be able to calculate sodium additions. Essentially, I decided to 
* Form BYO's article: <blockquote>All-grain brewers can use a single infusion mash and a low enough mash temperature so that the resulting beer does not end up too viscous. A temperature range of 148 to 154 ?F (64 to 68 ?C) works well. Use a lower mash temperature when using lower attenuating yeasts or high starting gravities and use a higher temperature when using the higher attenuating yeasts or lower starting gravity beers.</blockquote> This means that since I use Safale US-04, which is low attenuating, I'll use a low mash temperature; 65C should be enough. _Wasn't temp just bullshit?_
* Will add lactic acid and salts before heating (from Bru'N'Water): <blockquote>For best result, add acids prior to heating the water since heating can drive off a portion of the alkalinity that the acid addition was calculated to remove.</blockquote>
* As original recipe mentions, I'll target a 5.2 mash water pH (4.8 strike water pH).

Questions
=========

* There's a little bit less sodium that target profile.
    * Is this a problem
    * How can I add sodium (http://brulosophy.com/2018/01/22/water-chemistry-pt-10-the-impact-of-sodium-on-beer-exbeeriment-results/)?
    * https://www.themadfermentationist.com/2008/09/i-think-that-water-treatment-has-made.html
    * Which salt to use:
       * http://brulosophy.com/2018/01/22/water-chemistry-pt-10-the-impact-of-sodium-on-beer-exbeeriment-results/
       * https://onlinelibrary.wiley.com/doi/pdf/10.1002/j.2050-0416.1951.tb01621.x
       * From Bru'N'Water's [website](https://sites.google.com/site/brunwater/water-knowledge): <blockquote>Table Salt provides sodium and chloride ions and is readily soluble in water.  Non-iodized salt is preferred since iodine is poisonous to yeast.  Table salt is also known as sodium chloride and its chemical formula is: NaCl.  Table salt does not readily pick up moisture from the air.  Non-iodized table salt is available from grocery stores.  A table salt addition of 1 gram per gallon, increases the sodium content of the water by about 104 ppm and the chloride content by about 160 ppm.  An addition of 1 gram per liter, increases the sodium content of the water by about 393 ppm and the chloride content by about 607 ppm.</blockquote>
       * Iodized salt harms yeast?
       * canning salt
       * kosher salt
* Why 100 minutes of boil?
    * https://byo.com/article/boiling-advanced-brewing/
    * https://www.homebrewsupply.com/learn/60-90-otherwise-finding-best-boil-time.html
    * https://www.homebrewtalk.com/forum/threads/longer-boil-better-beer.295106/
* Right pH?
    * https://byo.com/article/the-dark-secrets-of-stout/
    * http://www.madalchemist.com/archives/mashing-the-perfect-sweet-stout/

Brew Notes
==========

* (17h50) Filling kettle
* (18h00) Kettle is leaking with the new valve. Had to empty and fill it again.
* (18h24) Fired kettle; water at 25C. I let the lid off to make sure chlorine. Started milling.
* (19h05) Mashing in. Went from 68C strike water temp to 66C with grains. It seems 22L is the max volume I can mash in that kettle.
* (20h08) Finished mashing. Wort at 65.7C, 17.8cm depth in the kettle. 1.042 preboil gravity at 65C. Started the boil.
* (20h45) Boil started. Put 20g of Columbus hop at 14.6% AA
* (21h59) Put hopstand hop; 70g of loose Cascade hop pellets) at 76C. Covered the kettle with the lid. After 30 minutes, I started the immersion chiller; The wort was at 66C then.
* (22h48) Transfered everying into the fermentor (with all trub) and oxigenized. 13 liters in the fermentor. 1.068 OG.
* (23h06) Poured yeast in. However, I pitched at 21C, which I think is a mistake. Tap water is too hot at this time of year. Next time, let's put the yeast in only on the next morning, giving time for the wort to cool to 15C.
* (24h00) Fully cleaned up the kitchen. 6 hours total.

Post-Brew Notes
===============

* I need to adjust batch target size in brewer's friend to validate the efficiency.

Bottling Notes (2018-07-21)
===========================

* Estimating 11 to 12 liters of beer. So, I'll consider 11.5L. Let's estimate 23C max temp of that beer. For 2.5 carbonation volume it gives 6.1g of sugar per liters, hence 70g of sugar.
* 11L, 70g of sugar, 1.016 FG. Gave 12x750mL, 5x330mL.
