---
title: "American Rye Stout"
output: github_document
---

This is the [second iteration](./brewlog_2018-06-28.md) of [Zymurgy Magazine's Stout Trousers](https://www.homebrewersassociation.org/homebrew-recipe/stout-trousers/). However, this time around the recipe is highly modified (to a point where it doesn't bear any resemblance) to become an American Rye Stout. This recipe was built and adjusted with [Brewer's Friend website](https://www.brewersfriend.com/homebrew/recipe/view/698901/american-rye-stout). The water profile adjustment by reading Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html) recipe.

The first recipe had a thin mouthfeel. To remedy that I decided to confirm a tendency this recipe had, meaning using rye as a "body builder".

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/american stout/brewlog.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

Water Information
=================

Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html) Water Profile:

* Calcium(Ca): 104.0 ppm
* Magnesium(Mg): 15.0 ppm
* Sodium(Na): 64.0 ppm
* Sulfate(SO4): 102.0 ppm
* Chloride(Cl): 76.0 ppm
* biCarbonate(HCO3): 280.0 ppm

Target Water Profile:

* Sodium: *100.0 ppm*
* Sulfate: 100.0 ppm
* Chloride: *150 ppm*
* Mash pH: 5.35

Water Additions:

* Gypsum: 1.5g
* Calcium Cloride: 0g
* Epsom Salt: 2.5g
* Lactic Acid (80%): 2ml
* Table Salt (non-iodized): 4.6g

Resulting Water:

* Calcium(Ca): 69.0 ppm
* Magnesium(Mg): 17.0 ppm
* Sodium(Na): 97 ppm
* Sulfate(SO4): 102 ppm
* Chloride(Cl): 150 ppm
* Bicarbonate: 100 ppm
* Estimated Mash pH: 5.33

Related Article/References
==========================

* Forum Question: [https://www.homebrewersassociation.org/forum/index.php?topic=7780.0](What hops with rye?)

Recipe Changes
==============

* Substracted some pale ale malt to rye malt (500g to 500g) to add mouthfeel and push a bit more the rye.
* Changed sodium target from 50ppm to 100ppm. This lead to a 150ppm cloride, but I won't try to change that. This is appropriate.
* Simplified the recipe by removing the belgian chocolate malt by some already included chocolate rye.
* Staggered the aroma hop to reflect Michael Tonsmeire's protocol (which was taken from Mitch Steele's).
* Changed estimated IBU contribution by aroma hop (was set to zero in previous recipe) but also lowered the IBU for that recipe. This should reduce significantly the biterness of that recipe.

Notes
=====

* https://www.homebrewtalk.com/forum/threads/sn-american-stout-water-profile.140344/
I remembered "designing great beers" having a water table for stouts so I looked it up.

They have london and dublin water profiles, the two classic styles for stouts. London water profile is considered best for imperial stouts so I'd recommend it for american as well.

Mineral: London, Dublin
Calcium: 50, 115
Magnesium: 20, 4
Sodium: 100, 12
Carbonate: 160, 200
Sulfate: 80, 55
Chloride: 60, 19



* Black Full in brewnwater

https://byo.com/article/add-body-to-your-beer/


http://univers-biere.net/br_flocons.php
https://www.brassageamateur.com/forum/ftopic3396-60.html
https://www.brassageamateur.com/forum/ftopic13884.html
https://www.brassageamateur.com/forum/ftopic16089-10.html
http://www.madalchemist.com/archives/mashing-the-perfect-sweet-stout/
http://beersmith.com/blog/2016/02/11/the-sulfate-to-chloride-ratio-and-beer-bitterness/

https://byo.com/article/adjuncts-explained/
https://byo.com/article/fabulous-foam/
https://byo.com/mr-wizard/steeping-oats-and-flaked-barley/
https://byo.com/article/maximizing-mouthfeel-tips-from-the-pros/
https://byo.com/article/using-munich-vienna-malts-tips-from-the-pros/
https://www.morebeer.com/articles/using_munich_malt
http://brulosophy.com/2017/12/11/grain-comparison-vienna-malt-vs-munich-malt-exbeeriment-results/
https://drinks.seriouseats.com/2012/11/what-does-pilsner-malt-taste-like-munich-vienna-2-row.html
https://www.winning-homebrew.com/malts.html
http://www.brew-dudes.com/munich-malt-flavor/815
https://byo.com/article/grain-on-the-brain/


Rye or Body:

* https://byo.com/article/brewing-with-rye-tips-from-the-pros/
* https://www.morebeer.com/articles/brewwithrye
* https://www.homebrewtalk.com/forum/threads/how-much-rye-is-too-much.243866/
* http://www.howtobrew.com/book/section-4/experiment/increasing-the-body
* https://knowledgeandpraxis.wordpress.com/2012/12/29/brewing-with-rye/
* http://allaboutbeer.com/article/rye-homebrew-recipes/

Make one small change per brew, omitting the change in the next brew if it doesn't get you closer to your target.

Carapils?

