---
title: "Zymurgy Magazine's Stout Trousers"
output: github_document
---

* https://www.brewersfriend.com/homebrew/recipe/view/659037/stout-trousers
* https://www.homebrewersassociation.org/homebrew-recipe/stout-trousers/
* https://byo.com/article/american-stout-style-profile/
* Water profile from Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html)

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/american stout/brewlog.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

Michael Tonsmeire's [Oatmeal Coffee Stout #3](https://www.themadfermentationist.com/2013/01/oatmeal-cofee-stout-3-bigger-and-bolder.html) Water Profile
----------------------------------------------------

* Calcium(Ca): 104.0 ppm
* Magnesium(Mg): 15.0 ppm
* Sodium(Na): 64.0 ppm
* Sulfate(SO4): 102.0 ppm
* Chloride(Cl): 76.0 ppm
* biCarbonate(HCO3): 280.0 ppm

Target Water Profile
--------------------

Water Additions:

* Gypsum: 1.5g
* Calcium Cloride: 1.8g
* Epsom Salt: 1g
* Lactic Acid (80%): 3ml
* Salt? 

Resulting Water:

* Calcium(Ca): 116.0 ppm
* Magnesium(Mg): 11.0 ppm
* Sodium(Na): 3 ppm
* Sulfate(SO4): 102.0 ppm
* Chloride(Cl): 72.0 ppm
* pH: 5.24

Questions
---------

* There's a little bit less sodium that target profile.
    * Is this a problem
    * How can I add sodium (http://brulosophy.com/2018/01/22/water-chemistry-pt-10-the-impact-of-sodium-on-beer-exbeeriment-results/)?
    * https://www.themadfermentationist.com/2008/09/i-think-that-water-treatment-has-made.html