---
title: "Speidel's Hefeweizen"
output: github_document
---


```{r setup-variables, echo=FALSE}

boiloff_rate_override = 4.0
brewlog_file = '../recipes/hefeweizen/brewlog_2020-01-18.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```


Water Information
=================

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 50ppm
    * Chloride: 75ppm
    * Mash pH: 5.30
* Water Additions:
    * 1.2g Gypsum
    * 0g Calcium Chloride 
    * 1.5g Epsom Salt
    * 9ml Lactic Acid (80%)
    * 3.6g Salt
* Adjusted Water Profile:
    * Calcium: 59ppm
    * Magnesium: 9ppm
    * Sodium: 50ppm
    * Sulfate: 48ppm
    * Chloride: 77ppm
    * Bicarbonate: 66ppm
    * Estimated Mash pH: 5.47

Preparation Notes
=================

Brew Notes
==========
* 38°C Mash in
* 45°C ferulic acid rest: 15 min 
* (55°C protein rest:5 min)
* 63°C maltose rest: 30 min
* 72°C saccharification rest: 30 min

Post Brew Notes
===============


Bottling Notes (2018-07-27)
===========================


