---
title: "Mad Fermentiationist's India Red Ale"
output: github_document
---


[original recipe](https://www.themadfermentationist.com/2011/04/india-red-ale-recipe.html), [mine](https://www.brewersfriend.com/homebrew/recipe/view/601663/mad-fermentationist-s-india-red-ale)

```{r setup-variables, echo=FALSE}

brewlog_file = '../india red ale/brewlog.xml'

```

```{r test-include, child = '../scripts/brewlog-template.Rmd'}
```

# Recipe Notes

* I'll use 75 minutes boiling time, as indicated in the recipe. I was wondering why, but the [following article](https://byo.com/article/boiling-advanced-brewing/) gave me the answer (For more information, look at the FAQ):<blockquote>When subjected to the temperature and agitation of boiling, complex reactions occur between sugars and amino acids, producing substances known as melanoidins. These are usually considered pleasant, resulting in flavors typically associated with the browning of meats and bread. Longer boiling times result in increased melanoidin production and are a major cause of wort darkening. It should be noted this is not quite the same thing as sugar caramelization, which requires higher temperatures and less water than what is present during boiling. Caramelization is part of the process that occurs during the production of crystal and other colored malts.</blockquote>What it means is that for that India Red Ale, is that we want more of those melaniodins.
* Given the following [article](https://byo.com/article/hop-stands/), I'll add the whirpool hop when I reach 78C and then let it cooldown the whole night.
* I'll add the dry hop loose as the [following article](http://brulosophy.com/2017/07/03/loose-vs-bagged-dry-hops-exbeeriment-results/) seems to point that it doesn't matter much (for my setup).
* I'll add the dry hopping in two pass: after 3 days of fermentation and 4 days before the end. I was scared about the "grassy taste", but [this article](http://brulosophy.com/2015/10/26/dry-hop-length-long-vs-short-exbeeriment-results/) put my mind to peace
* I've changed the pale chocolate malt from the original recipe to Weyermann's "Carafa Special I" (de-husked/unbittered). If you want more details on substitution, you can read the [following article](http://brulosophy.com/2017/08/07/roasted-grains-pt-3-carafa-special-ii-vs-chocolate-malt-exbeeriment-results/), but note that I put Carafa Special I, which color is closer to Briess' *pale* chocolate malt (but it's not going to be a problem here).
* Reading [this article](https://byo.com/article/the-science-of-step-mashing/), I thought about changing the mashing temp to 67 instead of using the two saccharification rest from the original recipe.


