---
title: "Mad Fermentiationist's India Red Ale"
output: github_document
---


[original recipe](https://www.themadfermentationist.com/2011/04/india-red-ale-recipe.html), [mine](https://www.brewersfriend.com/homebrew/recipe/view/645361/mad-fermentationist-s-india-red-ale-2018-03-23-)

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/india red ale/brewlog 2018-03-23.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

# Preparation Notes

* In the BIAB calculator, I've specified 1.5L of trub, even though I usually pour everything. However, I'm scared of the hop going in the fermenter. So, I'll really try to let 1.5 liters of trub in the kettle.
* For aroma hop, I won't put it in a hop bag, but rather use my BIAB bag to put it in it, as I do for malt. It will give a lot of space, but still be able to pick hop out of the word before racking.
* I wanted to use 75 minutes boiling time, as indicated in the recipe. I was wondering why, but the [following article](https://byo.com/article/boiling-advanced-brewing/) gave me the answer (For more information, look at the FAQ):<blockquote>When subjected to the temperature and agitation of boiling, complex reactions occur between sugars and amino acids, producing substances known as melanoidins. These are usually considered pleasant, resulting in flavors typically associated with the browning of meats and bread. Longer boiling times result in increased melanoidin production and are a major cause of wort darkening. It should be noted this is not quite the same thing as sugar caramelization, which requires higher temperatures and less water than what is present during boiling. Caramelization is part of the process that occurs during the production of crystal and other colored malts.</blockquote>What it means is that for that India Red Ale, is that we want more of those melaniodins. *However*, I still need to figure out what it means to have 75 minutes boil for BIAB. I probably need to add water just after mash out and start the boil. *For now*, let's put this aside.
* Given the following [article](https://byo.com/article/hop-stands/), I was tempted to add the whirpool hop when I reached 78C and then let it cooldown the whole night. However, reading some [newer](https://byo.com/article/save-hops-post-boil/) [articles](https://www.homebrewersassociation.org/how-to-brew/effect-post-boilwhirlpool-hop-additions-bitterness-beer/), it seems it's better to add whirpool hop right after flame out, cover the kettle and let it stay for 10 minutes. 
* I'll add the dry hop loose as the [following article](http://brulosophy.com/2017/07/03/loose-vs-bagged-dry-hops-exbeeriment-results/) seems to point that it doesn't matter much (for my setup, especially since I use 11L FastFerment conical fermenter).
* I'll add the dry hopping 4 days before the end (read [this article](http://brulosophy.com/2015/10/26/dry-hop-length-long-vs-short-exbeeriment-results/)).
* I've changed the pale chocolate malt from the original recipe to Weyermann's "Carafa Special I" (de-husked/unbittered), as mentionned by Michael Tonsmeire's recipe. If you want more details on substitution, you can read the [following article](http://brulosophy.com/2017/08/07/roasted-grains-pt-3-carafa-special-ii-vs-chocolate-malt-exbeeriment-results/), but note that I put Carafa Special I, which color is closer to Briess' *pale* chocolate malt (while the article talks about chocolate malt and Carafa Special II).
* Reading [this article](https://byo.com/article/the-science-of-step-mashing/), I thought about changing the mashing temp to 67 instead of using the two saccharification rest from the original recipe. Later on, reading [recipe's comments](https://www.themadfermentationist.com/2011/04/india-red-ale-recipe.html?showComment=1412987939054#c5460137782604240413), I got my confirmation it was okay: <blockquote>you'd likely be fine targeting a temperature around 152F for the duration!</blockquote>

# Notes

* Strike water: 14L at 65C (by mistake, was aiming 27C)
* This time also I didn't squeezed as much the bag to get all wort.
* Preboil gravity: 1.026 at 60C. However, since my other recipe hit their target, but this one had higher ABV and others had higher preboil gravity, I corrected boiling time. So, using [this](https://www.brewersfriend.com/hydrometer-temp/) calculator, 1.026 gravity at 60C gives 1.039 at 20C. Using [this](https://www.brewersfriend.com/dilution-and-boiloff-gravity-calculator/) calculator, to attain a 1.060 gravity, I had to boiloff 4.49L or 100 minutes (boiloff rate at 2.75). The difference in gravity might be due to mash low temp, but I suspect it's that I had a coarser mill of the grains this time, to plain on the safe side of tanin extraction (which I'm still not sure it's an issue). So, I should consider a lower brewer efficiency for next times.
* Preboil volume: Mesured 14.4cm kettle depth, estimating 12.84L of wort.
* Since volume is gonna be smaller, had to change the bittering hop to 15g. Came up with this (erroneous) calculation by weight_hop = (12.84 - 2.75) * 20 / 12.84. (but should have been (12.84 - (4.49 - 2.75)) * 20 / 12.84). The remaining 5g went into the aroma hop batch.
* Next time wait at the last minute to put the immersion cooler (and make sure it's stays in starsan until the last minute). This will allow an easier whirpool hopping by using the grain bag (BIAB) as hop sock (but with a LOT of space). This way the kettle lik will be able to rest on the kettle without letting warmth get out.
* OG: 1.058
* Fermenter: 7.75L, pourred all wort (with trub), but kept hop out (estimating 0.5L)
* Need to validate that the final volume fit with estimation (compared with last brew). Note that 14.4cm of preboil wort at 60C probably is less than 12.84L of wort when cold.
* (2018/04/03) Read gravity: 1.010
* (2018/04/03) Added dryhop. Didn't have any more cascade, so added Simcoe instead. 25g Centennial + 28 Simcoe (added a bit too much, but didn't wanted to put back the 3g)

# Bottling Notes (2018/04/08)

* Target carbonation: 3.0 -> 7.8g/L, 7.75L in fermentor, 1.5 yeast cake + 250mL of sugar water = 6.5 in racking container. 
* 50g of sugar in 250mL water (6.5 * 7.8)
* Gave 7 x 750mL bottles. Had to waste almost a 750 ml bottle. Next time make sure you have a normal bottle (330mL) for the end.

# TODO

* Note how changing the recipe from 60 minutes (target) to 100 minutes (actual) affected the volumes. I can use that to confirm my system variables. Normally the "total water needed" should stay the same.

