
---
title: "Rye Wit Session"
output: github_document
---

Recipe inspired from James Spencer's [Rye Wit Session](http://beerandwinejournal.com/rye-wit-session-beer). My [recipe](https://www.brewersfriend.com/homebrew/recipe/view/646277/rye-wit-session-ale).

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/rye wit session/brewlog.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```


# Preparation Notes

* I think I should have a lower "liquor-to-grist" ratio on this brew. I might not use the full volume to help alpha amylaze.
* For this recipe I want to keep a similiar hop profile than my american pale ale or american wheat ale (but not the IBU). This will allow us to compare the malt profile.
* Reading the following [article](https://www.themadfermentationist.com/2017/06/23-abv-session-neipa.html) from Michael Tonsmeire, I decided to go with the following water profile:
    * Cloride: 150ppm
    * Sulfate: 100ppm
    * Sodium: 50ppm
* I decided to go with 3% ABV to do a safer bet.

# Water Information

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 100ppm
    * Chloride: 150ppm
    * Mash pH: 5.35
* Water Additions:
    * 1.5g Gypsum
    * 2.99 Calcium Chloride (2.3g, but since it's 77%, 2.99g)
    * 2.5g Epsom Salt
    * 4.0ml Lactic Acid (80%)
    * 2.3g Salt
* Adjusted Water Profile:
    * Calcium: 113ppm
    * Magnesium: 17ppm
    * Sodium: 50ppm
    * Sulfate: 102ppm
    * Chloride: 155ppm
    * Bicarbonate: 34ppm
    * Estimated Mash pH: 5.38






