
---
title: "Rye Wit Session"
output: github_document
---

Recipe inspired from James Spencer's [Rye Wit Session](http://beerandwinejournal.com/rye-wit-session-beer). My [recipe](https://www.brewersfriend.com/homebrew/recipe/view/646277/rye-wit-session-ale).

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/rye wit session/brewlog.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```


# Preparation Notes

* I could seperate the water in two kettle to warm faster?
* I think I should have a lower "liquor-to-grist" ratio on this brew. I might not use the full volume to help alpha amylaze. *UPDATE* I won't do that, but it means the efficiency might be lower. So, 3.3% is good because if I'm going lower, it's okay.
* For this recipe I want to keep a similiar hop profile than my american pale ale or american wheat ale (but not the IBU). This will allow us to compare the malt profile.
* Reading the following [article](https://www.themadfermentationist.com/2017/06/23-abv-session-neipa.html) from Michael Tonsmeire, I decided to go with the following water profile (~BruNWater's Yellow Balanced):
    * Cloride: 60ppm
    * Sulfate: 75ppm
    * Sodium: 50ppm
* I decided to go with 4% ABV to do a safer bet.

# Water Information

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 75ppm
    * Chloride: 60ppm
    * Mash pH: 5.35
* Water Additions:
    * 3.1g Gypsum
    * 0g Calcium Chloride 
    * 0g Epsom Salt
    * 9.0ml Lactic Acid (80%)
    * 3g Salt
* Adjusted Water Profile:
    * Calcium: 79ppm
    * Magnesium: 4ppm
    * Sodium: 50ppm
    * Sulfate: 76ppm
    * Chloride: 77ppm
    * Bicarbonate: -60ppm?
    * Estimated Mash pH: 5.34






