---
title: "Mad Fermentationist's Standard American Pale Ale"
output: github_document
---

Original recipe from [Mad Fermentationist's blog](https://www.themadfermentationist.com/2012/07/standard-american-pale-ale-recipe-yeah.html), This is generated by exporting the recipe from [Brewer's friend](https://www.brewersfriend.com/homebrew/recipe/view/600614/mad-fermentationist-s-standard-american-pale-ale)



```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/american pale ale/brewlog 2018-03-31.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

# Notes

* From American Homebrewer's Association's blog, there's an [article](https://www.homebrewersassociation.org/how-to-brew/effect-post-boilwhirlpool-hop-additions-bitterness-beer/) that mentions that I can expect a 3.58% utilization with a 10 minutes whirlpool. This gives us 53.37 IBU, which is a lot for an American Pale Ale. However, as Michael Tonsmeire was saying: <blockquote>Despite around 50 IBUs, this beer should not be harshly bitter owing to the lower perceived bitterness of late additions.</blockquote>