---
title: "Modern Times Fortunate Island"
output: github_document
---

Inspiration from [here](https://www.themadfermentationist.com/2012/11/hoppy-wheat-with-march-pump-hoprocket.html) and [here](https://www.themadfermentationist.com/2014/03/fortunate-islands-homebrewed-yeast.html), [mine](https://www.brewersfriend.com/homebrew/recipe/view/654729/fortunate-island-2018-05-20).

For hop change, I used the following article: https://byo.com/article/american-wheat-style-profile/

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/american wheat ale/brewlog_2019-07-23.xml'
boiloff_rate_override = 4
#hop_price_override = 10.25

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

Water Information
=================

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 150ppm
    * Chloride: 150ppm
    * Mash pH: 5.35
* Water Additions:
    * 2.3g Gypsum
    * 4.50g Calcium Chloride (3.5g, but since it's 77%, 4.54g)
    * 7.5g Epsom Salt
    * 7.2ml Lactic Acid (80%) 
    * 3.5g Salt
* Adjusted Water Profile:
    * Calcium: 113ppm
    * Magnesium: 30ppm
    * Sodium: 50ppm
    * Sulfate: 152ppm
    * Chloride: 155ppm
    * Bicarbonate: 9ppm
    * Estimated Mash pH: 5.4

Brew Notes
==========



Post Notes
==========

Bottling Notes (2018/08/05)
==========================




