---
title: "Modern Times Fortunate Island"
output: github_document
---

Inspiration from [here](https://www.themadfermentationist.com/2012/11/hoppy-wheat-with-march-pump-hoprocket.html) and [here](https://www.themadfermentationist.com/2014/03/fortunate-islands-homebrewed-yeast.html), [mine](https://www.brewersfriend.com/homebrew/recipe/view/654729/fortunate-island-2018-05-20)

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/american wheat ale/brewlog_2018-07-22.xml'
hop_price_override = 10.25

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

Water Information
=================

* Target Water Profile:
    * Sodium: 50ppm
    * Sulfate: 150ppm
    * Chloride: 150ppm
    * Mash pH: 5.35
* Water Additions:
    * 1.6g Gypsum
    * 3.11g Calcium Chloride (2.4g, but since it's 77%, 3.11g)
    * 5.2g Epsom Salt
    * 4.0ml Lactic Acid (80%) (Was 5.0ml, but since I boiled the water before the mash, I decided to add less acid)
    * 2.4g Salt
* Adjusted Water Profile:
    * Calcium: 113ppm
    * Magnesium: 30ppm
    * Sodium: 50ppm
    * Sulfate: 152ppm
    * Chloride: 155ppm
    * Bicarbonate: 9ppm
    * Estimated Mash pH: 5.37

Brew Notes
==========

* (14h00) Prepared strike water. 24 liters is 22.6cm high in the kettle and water was at 24.6C. Warmed that water to remove chlorine. Stopped it at 75.2C.
* (17h50) Because of the evaporated water, it's now at 21.5cm, 41C. Readjusted water to get back at 22.6cm.
* (18h20) Mashing in at 67C. When down to 65.7C.
* (19h20) Getting the grains out. Wort is at 64.3C. Lost only 1.4C in one hour. 20.8cm at 63.1C. preboil gravity: 1.030. Firing kettle
* (20h20) Boil started.
* (21h20) Stopped kettle, cooled down wort to 72C for hop stand. I didn't have enough Amarillo and Citra, so here's the hops I used:
    * 25g Amarillo
    * 25g Citra
    * 25g Cascade
    * 10g Simcoe
* (21h25) Also, I reserved the following hops for the dry hop:
    * 25g Amarillo
    * 25g Citra
    * 35g Simcoe
* (21h50) Started immersion chiller. Brought wort at 32C and put it in fermentor. 15.5 liters. OG 1.052. I didn't pitch in the yeast yet. This is because the last degrees to 21C are taking too much water (since my tap water is at 21). I let the wort cooldown during the night.
* (22h35) Finished cleaning up everything.
* (7h30) Pitched yeast. Fermentor was at 18.2C.

Post Notes
==========

* Hop loose

Bottling Notes (2018/08/05)
==========================

* ~15.7L in the fermentor. Estimating 12L in the racking bucket. Estimated 20C on final fermentation temp.
* Target carbonation: 3.0 volume
* 7.7g of sugar per liter gives (* 12 7.7) = 92.4g of sugar.
* 1.010 FG


