---
title: "Modern Times Fortunate Island"
output: github_document
---

Inspiration from [here](https://www.themadfermentationist.com/2012/11/hoppy-wheat-with-march-pump-hoprocket.html) and [here](https://www.themadfermentationist.com/2014/03/fortunate-islands-homebrewed-yeast.html), [mine](https://www.brewersfriend.com/homebrew/recipe/view/654729/fortunate-island-2018-05-20)

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/american wheat ale/brewlog 2018-05-20.xml'
hop_price_override = 10.25

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

# Preparation Notes

* Readind the following article about [hop sock system](https://www.brewersfriend.com/forum/threads/using-a-hop-sock.155/), I realized that I could just use my BIAB bag has a hop sock. However, instead of tying it like a hop sock, just fit it on the kettle. I managed to do this for later recipe and it works quite well while doing whirlpool. However, I'm wondering if it wouldn't be better to have some false bottom or screen to get the bag to "sterilize" when boiling,without scorching/burning.
* I'll lower the IBU this time. I want to make sure I get more control over taste before using high IBU.
* I'll use [Michael Tonsmeire](https://www.themadfermentationist.com/p/contact-me.html) "[protocol](https://www.themadfermentationist.com/2014/03/fortunate-islands-homebrewed-yeast.html)" for hop stand: <blockquote> [Stagger] flame-out hop additions. Before adding the second dose, [allow] the wort to naturally cool for 15 minutes to preserve some of the heat-sensitive essential oils that are usually driven off with a standard hop-stand. </blockquote>
* At 60C, preboil gravity should be at 1.036.^[Calculated by brewersfriend.com's [Hydrometer Temperature Adjustment Calculator](https://www.brewersfriend.com/hydrometer-temp/)]
* Target Water Profile: Light colored an hoppy, but a bit sweet. Ideal Target: 75 ppm chloride, 175 sulfate. This has been taken from Michael Tonsmeire's article "Homebrew Water Treatment - A Practical Guide", adjusted having Michael's [water adjustment](https://www.themadfermentationist.com/2015/06/hop-juice-north-east-ipa-recipe.html?showComment=1444350236292#c7342676659099941542) in mind for NEIPAs. So, instead of pushing as much the chloride, I'll limit at 75 ppm for now. <blockquote>I don't think that water salts need to be exactly anything, but the general range is 100-200 PPM for both chloride and sulfate. I aim for more minerals (both) in lower gravity beers to compensate for less minerals from the malt. Otherwise it is to taste, 150/150 was about right for me in an APA/IPA. Chloride is part of the signature character of NEIPA compared to other IPAs, but it is more mouthfeel than juiciness (although that softness helps the juiciness of the hop and yeast esters along).</blockquote>

    * 12.8L of strike water
    * 2g gypsum
    * 2.6g calcium chloride (2g, but since it's 77%, 2.6g)
    * 2.5g epsom salt
    * 3.0ml lactic acid

# Brew Notes

* Started getting material out: 11h00
* Before warming water for strike: 14.1cm at 24.5C
* Fired kettle at 11h27
* Strike water temp 67.9, but went down to 65C
* Strike water ph at 26.9C had a 6.3pH (with salts and acid added)
* Wort pH of 5.7 (wort sample temp at 27C) after 10 minutes
* Mashing temp: 64/66 C. This is a bit lower than I the target 67C.
* Preboil gravity 1.041
* Fired kettle for boiling wort at 13h12
* Kettle height 12.9cm at 65C before boil.
* Added 17g of Mosaic on top of already specified aroma hop. This was some left overs that I had to use. 
* Put aroma hops at 70C for 30 minutes
* Next time I'll leave the aroma hop loose in the kettle and, as usual, I'll transfer everything in the fermentor.
* Preboil gravity was 1.031 at 60C, which is WAY lower than the "expected" 1.036 from [brewer's friend calculator](https://www.brewersfriend.com/hydrometer-temp/), but which ended up being WAY above the actual expected 1.034 preboil gravity at 20C from brewer's friend.
* OG: 1.059, Volume in fermenter: 8.5L, finished at 15h32
* Recipe was done with a 62% efficiency in mind (which reflect my last efficiencies), which would have given a 5.26% ABV. However, since I improved the pH AND stirred the mash more often, I ended up with a higher efficiency of 75%. I didn't try to correct it; 6.3% ABV will do. Note that I didn't "double crush" the grains to mill it almost to flour.
* Target fermentation temperature is 15C. I'm trying to follow Drew Beechum's and Denny Conn's (from [Experimental Brew](https://www.experimentalbrew.com/)) advice and trying to hit the lower end of Safale US-05's temperature range.

# Post Brew Day Notes

* 2018/06/10 9h00: Put dry hop into fermenter (25g Amarillo + 25g Citra) and changed yeast jar (500 ml jar). I would have done it after two of fermentation, but I didn't managed to get to it.