---
title: "Modern Times Fortunate Island"
output: github_document
---

```{r setup-variables, echo=FALSE}

brewlog_file = '../recipes/american wheat ale/brewlog 2018-03-17.xml'

```

```{r test-include, child = '../../scripts/brewlog-template.Rmd'}
```

# Notes

* Volume: 16.2, depth: 18.4cm
* (17h30) Stated the kettle (temp 35C)
* (18h00) Water ready at 68C (after steering), put grains gradullary to avoid dough balls. Note that thermometer was should 75C. Need to have better thermometer.
* (19h30) After 90 minutes mash, fired up the kettle. Depth was 17.6 cm. (note that for the depth I never checked the temperature, since it [expands](https://www.engineeringtoolbox.com/volumetric-temperature-expansion-d_315.html))
* Preboil gravity: 1.018 (still warm).
* (20h05) Wort boilling roll started. There was a bit of boil over (kettle lid was on to get hot quickly).
* (20h50) Put bittering hop, 6g of Columbus. Total boil time was 1h45. 
* (21h50) Flame out, put whirlpool hop and kettle lid (25g Mosaic, 25g Cascade, 11g Amarillo). Waited for 10 minutes.
* (22h00) Started wort chilling.
* (22h15) Wort at 21C. Took final gravity from trub. Wort in fermenter 10.8L, OG: 1.040. Boiloff rate calculation must be wrong. Need to check. In my calculation I put trub size, but it was zero in previous recipe. Estimation of preboil volume is 15.31, but it's was 15.85 (but might be okay since it needs to be temperature corrected). Need to recheck size with 20C water.
* I let the hop cones free in the wort. Caused my grief when tried to rack in the fermenter. I broke my auto siphon. Next time just put the grain bag and add the hop in it.
* (8h) Temp of cooler was 16C. Might be too cold. Fermentation didn't started. Will see tomorrow morning.

# Bottling Notes (01/04/2018)

* Target carbonation: 3.0. 7.8g/L. 10.8L in fermentor, 1.5 yeast cake + 250mL of sugar water = 9.5 in racking container. (managed to get only 9L because I spilled some wort)
* 74g of sugar in 250mL water.
* Gave 11 x 750mL bottles.

# Tasting Notes (24/04/2018)

* Appearance - Straw color, a bit of hazyness.
* Smell - Delicate peach and apples aroma. Gives a hint of acidity.
* Taste - Bitterness a bit too present compared to the rather absence of hop flavor. Acidity (probably due to the wheat) is appreciable though. 
* Mouthfeel - A tad too watery to my taste, probably due to the low ABV. Good carbonation, but I'm surprised that the bubbles seems pretty big compared to what I'm used to. Might be due to low ABV?
* Drinkability & Notes - This is still the best beer I made to date. However, I need to improve my aroma hop utilization. Higher ABV and better aroma should make it a very good summer/"after hard work day" beer.

# TODO

* Batch volume isn't the targetted one. Efficiency neither. Need to revisit those numbers.
* Need to try hop stand at 170F/76C for 30 minutes, rather than 98C for 10 minutes.
* There's too much yeast in bottom of bottles, I really need to improve my "racking" so that I transfert less yeast into bottles. Right now I use huge 30L buckets to ferment, but containing only 9L of beer. This means that I have a large yeast cake surface contact with beer. Need to have more suitable equipment for 9L batches.
