---
title: "Modern Times Fortunate Island"
output: github_document
---

```{r setup-variables, echo=FALSE}

brewlog_file = '../macgyvers-island/brewlog 2018-03-17.xml'

```

```{r test-include, child = '../scripts/brewlog-template.Rmd'}
```

# Notes

* Volume: 16.2, depth: 18.4cm
* (17h30) Stated the kettle (temp 35C)
* (18h00) Water ready at 68C (after steering), put grains gradullary to avoid dough balls. Note that thermometer was should 75C. Need to have better thermometer.
* (19h30) After 90 minutes mash, fired up the kettle. Depth was 17.6 cm. (note that for the depth I never checked the temperature, since it [expands](https://www.engineeringtoolbox.com/volumetric-temperature-expansion-d_315.html))
* Preboil gravity: 1.018 (still warm).
* (20h05) Wort boilling roll started. There was a bit of boil over (kettle lid was on to get hot quickly).
* (20h50) Put bittering hop
* (21h50) Flame out, put whirlpool hop and lid. Waited for 10 minutes.
* (22h00) Started wort chilling.
* (22h15) Wort at 21C. Took final gravity from trub. Wort in fermenter 10.8L, OG: 1.040. Boiloff rate calculation must be wrong. Need to check. In my calculation I put trub size, but it was zero in previous recipe. Estimation of preboil volume is 15.31, but it's was 15.85 (but might be okay since it needs to be temperature corrected). Need to recheck size with 20C water.
* (8h) Temp of cooler was 16C. Might be too cold. Fermentation didn't started. Will see tomorrow morning.