
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars, include=FALSE}
library(rvest)
library(xml2)

source("biab-calculator.R")

# retrieve the xml recipe
beerxml_output <- read_xml("brewlog.xml")

batch_size <- xml_double(xml_find_first(beerxml_output, xpath='//BATCH_SIZE'))
grain_weight <- sum(xml_double(xml_find_all(beerxml_output, xpath='//FERMENTABLES/*/AMOUNT')))
grain_temp <- xml_double(xml_find_first(beerxml_output, xpath='//MASH/GRAIN_TEMP'))
mash_temp <- xml_double(xml_find_first(beerxml_output, xpath='//MASH/MASH_STEPS/*/STEP_TEMP'))
boil_time <- xml_double(xml_find_first(beerxml_output, xpath='//BOIL_TIME'))


recipe <- create_metric_recipe(grain_weight, grain_temp, batch_size, mash_temp, boil_time, system_variables)
```


* [BIAB Calculator](http://www.biabcalculator.com/)
    * Recipe Parameters
        * Grain Bill: `r recipe$grain_weight` Kilograms
        * Grain Temp: `r recipe$grain_temp` Celsius
        * Batch Size: `r recipe$batch_size` Liters
        * Mash Temp: `r recipe$mash_temp` Celsius
        * Boil Time: `r recipe$boil_time` Minutes
    * System Variables
        * Kettle Size: `r recipe$kettle_size` Liters
        * Trub: `r recipe$trub_size` Liters
        * Boiloff Rate: `r recipe$boiloff_rate` Liters/Houree
        * Grain Absorption: `r recipe$grain_absorption` Liters/Kilograms of grain
    * Output
        * Total Water Needed: `r round(get_water_needed(recipe), 2)` Liters
        * Strike Water Temp: `r round(get_strike_water_temp(recipe), 1)` Celsius
        * Total Mash Volume: `r round(get_total_mash_volume(recipe), 2)` Liters
        * Preboil Wort: `r round(get_pre_boil_wort_volume(recipe), 2)` Liters
        * Postboil Wort: `r round(get_post_boil_wort_volume(recipe), 2)` Liters
        * Into Fermenter: `r round(get_fermenter_volume(recipe), 2)` Liters
        
```{r kable, echo=FALSE}

library(xml2)
library(knitr)

data <- XML::xmlParse('brewlog.xml')
fermentables <- XML::xmlToDataFrame(nodes = XML::getNodeSet(data, "//FERMENTABLES/*"), stringsAsFactors = FALSE, colClasses=c("character", "integer", "character", "double", "double", "double", "character", "character"))

hops <- XML::xmlToDataFrame(nodes = XML::getNodeSet(data, "//HOPS/*"), stringsAsFactors = FALSE, colClasses=c("character", "integer", "double", "double", "character", "character", "integer", "character", "double", "double"))
hops$TIME <- as.difftime(hops$TIME, units="mins")

kable(fermentables)
kable(hops)

```
