
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
source('brewlog-template.R')

```

# Recipe

* Method: BIAB
* Style: `r style`
* Batch Size: `r batch_size` Liters (fermentor volume)  
* Boil Gravity: TODO (recipe based estimate)  
* Efficiency: `r efficiency`% (brew house)  
* Source: `r recipe_source`
* Original Gravity: `r original_gravity` 
* Final Gravity: `r final_gravity`
* ABV (standard): `r abv`%
* IBU (tinseth): `r ibu`
* SRM (morey): `r srm`

# Fermentables 

```{r kable-fermentables, echo=FALSE}

kable(fermentables)

```

# Hops 

```{r kable-hops, echo=FALSE}

kable(hops)

```

# BIAB Calculator

Since I use BIAB (Brew in a Bag) method, here's the calculations taken from [BIAB Calculator](http://www.biabcalculator.com/)

## Recipe Parameter

* Grain Bill: `r recipe$grain_weight` Kilograms
* Grain Temp: `r recipe$grain_temp` Celsius
* Batch Size: `r recipe$batch_size` Liters
* Mash Temp: `r recipe$mash_temp` Celsius
* Boil Time: `r recipe$boil_time` Minutes
    
## System Variables

* Kettle Size: `r recipe$kettle_size` Liters
* Trub: `r recipe$trub_size` Liters
* Boiloff Rate: `r recipe$boiloff_rate` Liters/Houree
* Grain Absorption: `r recipe$grain_absorption` Liters/Kilograms of grain
    
## Recipe Output

* Total Water Needed: `r round(get_water_needed(recipe), 2)` Liters
* Strike Water Temp: `r round(get_strike_water_temp(recipe), 1)` Celsius
* Total Mash Volume: `r round(get_total_mash_volume(recipe), 2)` Liters
* Preboil Wort: `r preboil_wort_volume` Liters
* Postboil Wort: `r postboil_wort_volume` Liters
* Into Fermenter: `r round(get_fermenter_volume(recipe), 2)` Liters
        
